**Density Dependence**

### 2023-02-09 Rmd/ddWhb.Rmd
copied from ddMac

---
title: "**Density Dependence**"
subtitle: "Mackerel: density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE

@@

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/mac/dd/",
               fig.path  ="../tex/figs/mac/dd/",
               fig.width =8,
               fig.height=6,
               dev       ="png")

@@

```{r, eq}
par=teleost[c("linf","k","t0","l50","a","b"),dimnames(teleost)$iter=="Scomber scombrus"]
par=lhPar(par,m1=0.2/(300^-0.288),m2=-0.28,m3=NA)
eq =lhEql(par,m="lorenzen")
```

>>>>

---
title: "**Density Dependence**"
subtitle: "Blue Whiting: density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE

@@

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/whb/dd/",
               fig.path  ="../tex/figs/whbdata/dd/",
               fig.width =8,
               fig.height=6,
               dev       ="png")

@@

```{r, eq}
par=teleost[c("linf","k","t0","l50","a","b"),dimnames(teleost)$iter=="Micromesistius poutassou"]
par=lhPar(par,m1=0.2/(300^-0.288),m2=-0.28,m3=NA)
eq =lhEql(par,m="lorenzen")
```
